\begin{enumerate}
\item Attributes
-- Defines attributes by name.
\item Courses
-- Defines courses by name with the servings.
\item DayPlans
-- Deprecated.
\item Dietition
-- Defines users with elevated permissions.
They differ from standard users only in that they can prescribe dietary
recommendations.
\item Emails
-- Defines emails per user.
Each email is unique to a user.
\item Ingredients
-- Defines ingredients by name.
For example,
cooking items such as salt, pepper, oil, eggs, and wafles are all ingredients.
\item IngredientsCourses
-- Defines a relationship between ingredients and courses.
There are two attributes corresponding to the public keys of
each table respectively, of course.
\item Meals
-- Defines meals by names.
Meals are made of courses.
For example,
the American breakfast consists of eggs, bacon, and sausage.
\item UserSelectedMeals
-- Defines meals that appear on a user's schedule for a specific day.
\item MealsCourses
-- Defines the many to many relationship between meals and courses.
\item MealsFoodAttributes
-- Defines the many to many relationship between meals and attributes.
\item Prescription
-- Defines a dietary description for a user and made on a certain date.
\item PrescriptionAttributes
-- Defines a many to many relationship between prescription and attributes.
\item Ratings
-- Defines a many to many relationship between users and meals with a rating from 0 to 5 stars.
\item UserType
-- Defines different types of users.
We are not sure of the user for this, yet.
This table maybe deprecated.
\item Users
-- Defines a user with a first name, last name, user name, gender,
password, and user type.
The user type attribute may be deprecated soon.

\end{enumerate}
